---
title: "STAT605_final_proposal_Group2"
author: "Zhengda Liu"
date: "2024-10-31"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataset Introduction

- NYC Real-Time Traffic Speed Data

- 24GB dataset on Kaggle
https://www.kaggle.com/datasets/aadimator/nyc-realtime-traffic-speed-data

- Contains ‘real-time’ traffic information, including average speed, travel time and location of speed detectors

## Questions
#### Question0: Exploratory Data Analysis: deep in the dataset

#### Question1: How to quantize the over-speed feature?

#### Question2: Which streets in New York have a higher rate of vehicles over speed?

## Data Description

- 64 million samples and 13 variables in this dataset

- Care about “id” “speed” “link_id” “borough” “link_name” variables
"borough" represents the name of the New York district, including Brooklyn, Bronx, Manhattan, 

- Queens and Staten Island

- "link_name" represents the names of the streets

## Data Split: Divide dataset by “LINK_ID” into 160 small dataset

```{r,eval = FALSE}
mydata = read.csv("DOT_Traffic_Speeds_NBE.csv", header = TRUE)
linkid = unique(mydata$LINK_ID)
for(i in linkid){
  newdata = mydata[mydata$LINK_ID==i, ]
  write.csv(newdata, paste("linkid_", as.character(i), ".csv", sep=""), row.names=FALSE)
}
```

```{r}
mydata = read.csv("linkid_4329472.csv", header = TRUE)
mydata_head=mydata[1:5,c(1,2,6,12,13)]
head(mydata_head)
```

## EDA part

...


## quantize the over-speed feature and jam feature
$$\ \text{Overspeed Rate =}\frac{\sum_{i}{I(s_i > 60)}}{m} \\$$
$$\ \text{Jam Rate =}\frac{\sum_{i}{I(s_i = 0)}}{m} \\$$
$$\  \text{m  is  the  number  of  cases  in  the  file.}  \\$$
$$\ s_i  \text{  is  the  speed  of  the  }i_{th}\text{ case  in  the  file.} $$

## 

```{r}
sum(mydata["SPEED"]>60)/nrow(mydata)
```

- The rate of vehicles’exceeding speed passing on this streets is 0.021%.